---
title: "R_BrdgWrkshp_Week1_Quiz_02"
author: "Vinayak Kamath"
date: "12/21/2019"
output: html_document
---


## 1. Write two functions. These functions should take a numeric vector as input, and determine the mean and the median from the values in the vector. Please do not use the built-in mean() or median() functions. You should also provide some code that initializes your numeric vector and calls your two functions!: 

-> Function to do the actual calculation
``` {r include= TRUE}
get_mean <- function(inp_vector)
{
  return (sum(inp_vector) / length(inp_vector))
}

get_median <- function(inp_vector)
{
  med_point <- length(inp_vector)/2
  inp_vector_sort <- sort(inp_vector, decreasing = FALSE)
  return ( ifelse( length(inp_vector_sort) %% 2 != 0 ,  inp_vector_sort[round(med_point, digits=0)] 
           , (inp_vector_sort[med_point] + inp_vector_sort[med_point + 1] ) /2 ))
}
```


-> input values from Users and convert to numeric vector
``` {r}
inp.number <- readline("Enter NUmbers: ")
inp.number <- "12, 56, 12, 45, 35, 56, 0, 12"
inp.number.vector <- as.numeric(unlist(strsplit(inp.number, ",")))

inp.number.vector
```

-> call the functions for the given vector
``` {r}
do.call("get_mean", args=list(inp.number.vector))
mean(inp.number.vector)
do.call("get_median", args=list(inp.number.vector))
median(inp.number.vector)
```



