---
title: "R_BrdgWrkshp_Week2_Assignment"
author: "Vinayak Kamath"
date: "12/29/2019"
output: html_document
---

Data sets: http://vincentarelbundock.github.io/Rdatasets/ (click on the csv index for a list): datasets.csv

"Stat2Data","AppleStock","Daily Price and Volume of Apple Stock",66,4,0,0,1,0,3,
"https://raw.github.com/vincentarelbundock/Rdatasets/master/csv/Stat2Data/AppleStock.csv",
"https://raw.github.com/vincentarelbundock/Rdatasets/master/doc/Stat2Data/AppleStock.html"


### 1. Use the summary function to gain an overview of the data set. Then display the mean and median for at least two attributes:

```{r}
library(readr) 
apple.data <-read_delim(file="AppleStock.csv",  delim=',') 
apple.data 

summary(apple.data)
```
-> Mean and Median of Attribute Price:
```{r}
round(mean(apple.data$Price), digits=2)
round(median(apple.data$Price), digits=2)
```
-> Mean and Median of Attribute Volume: 
```{r}
round(mean(apple.data$Volume), digits=2)
round(median(apple.data$Volume), digits=2)
```


### 2. Create a new data frame with a subset of the columns and rows. Make sure to rename it:

-> Creating asubset having only August 2016 Data in it ; and selected columns:
```{r}
apple.data.august2016 <- subset(apple.data, grepl("^8", apple.data$Date) & grepl("2016$", apple.data$Date)  , select = c("X1","Date","Price","Change"), drop = FALSE )

apple.data.august2016
```


### 3. Create new column names for the new data frame:
-> Renaming the column names
```{r}
names(apple.data.august2016) <- c("X1"= "Id", "Date" ="MarketDate","Price" = "StockPrice", "Change" ="PriceChange")
apple.data.august2016
```


### 4. Use the summary function to create an overview of your new data frame. The print the mean and median for the same two attributes. Please compare:
-> USe of summary on the new data set: 
```{r}
summary(apple.data.august2016)

round(mean(apple.data.august2016$StockPrice), digits=2)
round(median(apple.data.august2016$StockPrice), digits=2)

round(mean(apple.data.august2016$PriceChange), digits=2)
round(median(apple.data.august2016$PriceChange), digits=2)
```


### 5. For at least 3 values in a column please rename so that every value in that column is renamed. For example, suppose I have 20 values of the letter “e” in one column. Rename those values so that all 20 would show as “excellent”:

-> Adding a new Column having character values:
```{r}
apple.data.august2016$ChangeIndicator = ifelse(apple.data.august2016$PriceChange > 0 , "I",(ifelse(apple.data.august2016$PriceChange <0, "D", "S" )) )

apple.data.august2016
```
-> Column Value Renaming:
```{r}
apple.data.august2016$ChangeIndicator <- gsub("I","Increase", apple.data.august2016$ChangeIndicator)
apple.data.august2016$ChangeIndicator <- gsub("D","Decrease", apple.data.august2016$ChangeIndicator)
apple.data.august2016$ChangeIndicator <- gsub("S","Same", apple.data.august2016$ChangeIndicator)

apple.data.august2016
```


### 6. Display enough rows to see examples of all of steps 1-5 above:
-> Data:
```{r}
as.data.frame(apple.data)
as.data.frame(apple.data.august2016)
```


### 7. BONUS – place the original .csv in a github file and have R read from the link. This will be a very useful skill as you progress in your data science education and career:
-> Access csv fiel via github:
```{r}
theURL <-  "https://raw.githubusercontent.com/kamathvk1982/CunyBridgeR/master/AppleStock.csv"
git.apple.data <-read_delim(file=theURL,  delim=',') 
git.apple.data 

summary(git.apple.data)

```


