---
title: "R_BrdgWrkshp_Week2_HandsOn"
author: "Vinayak Kamath"
date: "1/5/2020"
output: html_document
---

1. Load the diamonds dataset, which is included with the ggplot2 package.  Identify which variables in the diamond set are numeric, and which are catgorical (factors).
``` {r}
library(ggplot2)
str(diamonds)
```


2. Generate summary level descriptive statistics:  Show the mean, median, 25th and 75th quartiles, min, and max for each of the applicable variables in diamonds.
``` {r}
summary(diamonds)

summary(diamonds$carat)
quantile(diamonds$carat)
```


3. Determine the frequency for each of the diamond colors.
```{r}
table(diamonds$color )
with (diamonds, table(color))
```


4. Determine the frequency for each of the diamond cuts, by color
```{r}
table(diamonds$cut, diamonds$color  )
with (diamonds, table(cut, color))
```

5. Create a graph for a single numeric variable.
```{r}
hist(diamonds$carat , main = 'Diamonds Carat Data' )
boxplot(diamonds$carat , main = 'Diamonds Carat Data')
table(diamonds$cut )
pie(table(diamonds$cut ))
```


6. Create a scatterplot of two numeric variables. 
```{r}
scatter.smooth(x=diamonds$carat, y=diamonds$price)
plot(diamonds$price ~ diamonds$carat)
qplot(carat, price, data=diamonds)
ggplot(diamonds,  aes(x=carat, y=price) ) +  geom_point()
```

