---
title: "R_BrdgWrkshp_Week1_Assignment"
author: "Vinayak Kamath"
date: "12/21/2019"
output: html_document
---

# 1. Write a loop that calculates 12-factorial:

-->  Function to calculate factorial of a number passed as arguement
```{r include= TRUE}
get.factorial <- function(input.num = "0", ...)
{
  if(is.integer(as.integer(input.num)) && input.num >= 1)
  {
    ret_fact<- 1
    for (i in 1:input.num)
      ret_fact <- ret_fact * i
  }else
  {
    return ('Not a valid Number Passed !')
  }
  return ( ret_fact)
}

```

-->  Get the factorial by passign the input value
```{r}
get.factorial(12)
```



# 2. Show how to create a numeric vector that contains the sequence from 20 to 50 by 5:

-->  Function to return a sequence
```{r}
get.sequence_vector <- function(start, end, interval, ...)
{
  return (seq(from=start, to=end, by=  interval))
}
```

-->  Get the numeric vector by passign the input value
```{r}
get.sequence_vector(start=20, end=50, interval= 5)
```



# 3. Create the function “quadratic” that takes a trio of input numbers a, b, and c and solve the quadratic equation. The function should print as output the two solutions.

-->  Function to solve the quadratic equation
```{r}
quadratic <- function(a, b, c, ...)
{
  x1 <-  ( -(b) + sqrt((b ^ 2 ) - (4 * a * c))  ) / (2*a)
  x2 <-  ( -(b) - sqrt((b ^ 2 ) - (4 * a * c))  ) / (2*a)
  sprintf ("x is equal to %s or %s", x1, x2)
}
```

-->  Get the input 1
```{r}
inp.a <- 10
inp.b <- 12
inp.c <- 2

quadratic(a = inp.a, b = inp.b, c = inp.c)
```


-->  Get the input 2
```{r}
inp.a <- 5
inp.b <- 6
inp.c <- 2

quadratic(a = inp.a, b = inp.b, c = inp.c)
```
